---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = "ragg_png"
)
```

# cards

<!-- badges: start -->
`r badger::badge_license("MIT", "blue", "https://cran.r-project.org/web/licenses/MIT")`
`r badger::badge_repostatus("active")`
<!-- badges: end -->

The goal of cards is to ...

## Installation

You can install the development version of cards like so:

``` r
# pak::pkg_install("elipousson/cards")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(cards)
```

cards includes data on standard page sizes including sizes for papers, photo prints, postcards, and playing cards.

```{r get_page}
get_paper("Letter")

get_paper("Letter", orientation = "landscape")

get_card("Poker")
```

cards uses ggplot2 to create plots for individual cards and patchwork to assemble card plots into page layouts for print.

```{r plot_cards}
cards <-
  plot_cards(
    "Poker",
    n = 8,
    number = TRUE,
    border = TRUE,
    size = 4,
    linewidth = 0.5,
    text = rep(c("\U2664", "\U2661", "\U2662", "\U2667"), 2), # "♤", "♡", "♢", "♧" 
    color = "yellow"
    )

cards[[1]]
```

```{r layout_cards}
layout_cards(cards, paper = "Letter", orientation = "landscape")
```

cards currently has very limited features but additional features are expected to include multi-page layouts, control over the position of card elements, preset card formats/designs, and appropriate handling of cut-lines for DIY card printing.

